---
title: "Data Science for Education with .red[**R**]"
subtitle: "First class"
author: "Yangyong Ye"
date: "2018/11/13"
output:
  xaringan::moon_reader:
    css: [default,zh-CN.css,mycss.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

class: center, middle,inverse

# Let's begin ou.red[**R**] journey!
---
class: center, middle,inverse

# Why Language?

## Fast
## Powerful
## Note-taking
## Reproducible

---
class: center, middle,inverse

# R
### small
### versatile
### beautiful
### not hard to learn

???

In this slide, I will talk about the advantages of R and why I change from spss to R.

---
class: inverse, middle
# Course Overview
- Environment Preparation

- Data fetching

- Data preparation

- Data tabulation

- Data visulization

- Data analysis

- Data creation

---
class: center middle

# Class Schedule
```{r,echo=FALSE, fig.width=10}
library(timevis)
classplan <- data.frame(
  id = 1:8,
  content =c("week 1: \nintroduction", "week 2: data preparation", "week 3: data tabulation", "week 4: data visualization I",
             "week 5: data visualization II", "week 6: data analysis", "week 7: data analysis", "week 8: data creation"),
  start= c("2018-11-13","2018-11-20","2018-11-27","2018-12-4","2018-12-11",
           "2018-12-18","2018-12-25","2019-01-01")
)


timevis(classplan,
        options = list(width = "800px",height="400px"))
```



---
class: inverse, middle

# Preparation

- Environment Preparation

  - RStudio installation
  
  - RStudio introduction
  
  - R introduction
  
  - Common package installation (eg. **tidyverse**)
  
  - Self-learning material [R for data science](http://r4ds.had.co.nz/)

---
class: inverse, middle
# Data Fetching
- SOURCE

  - 中国教育追踪调查[CEPS](http://ceps.ruc.edu.cn/)
  - 中国家庭追踪调查[CFPS](http://www.isss.pku.edu.cn/cfps/)
  - 中国社会综合调查[CGSS](http://cgss.ruc.edu.cn/)
  - 中国家庭收入调查[CHIP](http://ciid.bnu.edu.cn/chip/index.asp)
  - 中国健康与营养调查[CHNS](https://www.cpc.unc.edu/projects/china)
  - 中国教育统计年鉴[EDU_STAT](http://data.cnki.net/yearbook/Single/N2017120244)
  - 中国教育经费统计年鉴[EDU-FINA](http://data.cnki.net/yearbook/Single/N2018070117)
  

---
class: middle,inverse
# Data Preparation

- Data Manipulation

  - recode/rename
  
  - subset(select/filter)
  
  - join/combine
  
  - arrange
  
  - summarize
  
  - reshape

---
class: middle,inverse
# Data Tabulation

- Table Type

  - frequency table
  
  - crosstable
  
  - summary table
  
  - table formating<sup>*<sup>
  
  - test-table(t, chi, anovo)
  
  - regresion table

.footnote[[*]this will use kableExtra package]

---
class: inverse, middle

# Data Visualiztion

- [Graph Type](https://www.r-graph-gallery.com/)

  - **Rankings**: Barplot,circular barplot, Spider/Radar, parallel, lollipop/stem, circular barplot
  
  - **Distribution**: histgram, density, boxplot, violin, ridgeline/joyplot
  
  - **Correlation**: scatter, heatmap, correlogram, bubble, connected scatter, density 2D
  
  - **Composition**: treemap, dendrogram, venn diagram, stacked bar, pie chart, doughnut, circular packing

---
class: inverse, middle

# Data Visualiztion

- [Graph Type](https://www.r-graph-gallery.com/)

  - **Evolution**: line, Area, stacked area, streamgraph, parallel, time series
  
  - **Maps**: background map, connection, choropleth, bubble, hexbin map, cartogram
  
  - **Flow**: network, chord diagram, hierarchical edge bundling, sankey diagram
  
  - **Other**: interactive, animation, 3d, color, cheat sheet.

---
class: middle,inverse

# Data Visualiztion

- Useful packages

  - comprehensive package: **ggplot2**

  - for dendrogram: **packcircles**,**ggraph**, **treemap**, **dendextend** 

  - for network: **igraph**,**tidygraph**,**ggraph**

  - correlation matrix: **ellipse**, **car**, **GGally**,**corrgram**

  - flow diagram: **ggalluvial**


---
class: inverse, middle,center

# Intentionally blank

---
class: middle,inverse
# Data Analysis

- Data analysis ladder

  - simple test(**t**, *chi*, anova)

  - correlation
  
  - factor analysis
  
  - cluster analysis

  - regresion

---
class: middle,inverse

# Logistics
- MATERIALS

  - Garrett Grolemund, Hadley Wickhan. [R for data science](https://r4ds.had.co.nz/)
  - Hadley Wickham, Ggplot2-Elegant-Graphics for Data Analysis(2nd), Springer.
  - 王孝玲,教育统计学,华东师范大学出版社.
  - Other(TBC)

- ACCESSMENT
  - Presence      (10%)
  - Project       (20%)
  - Homeworks     (30%)
  - Final         (40%)
 
  
---
class: middle,inverse, center

# Project Example

### 学生惩戒
### 财政年报
### 建档立卡学生就学报告
### 高考成绩分析报告

---

class: middle, inverse, center

# Homework for .red[NEXT] Week

## Chapter 1-5 from Doc. Wang
## Chapter 5, 12, 13, from R4DS
## CEPS
---
# for Rstudio

package installation, for example *tidyverse*
use *mpg* to make some example.
what is script?
what is project?

```{r}
#install.packages("tidyverse")
library(tidyverse)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```

